This is an example of article title

### 2019-05-30 paper/paper.tex
experiment plots
complexity curves

\section{Experiments}
\label{sec:experiments}
%
\section{Conclusion}
\label{sec:conclusion}
%

>>>>

\section{Experiments}
\label{sec:experiments}
%
\begin{figure}[htb]
\centerline{\includegraphics[width=0.99\linewidth]{fig/chipsort-bench-8k.pdf}}
\centerline{\includegraphics[width=0.99\linewidth]{fig/chipsort-bench-256k.pdf}}
\caption{Empirical CDF from {\tt chipsort\_medium!} with 8k {\tt UInt32} values and {\tt chipsort\_large} with 256k values. Results from 10,000 measurements. Speedups are 14\% and 3\%.}
\label{fig:bench-cdf}
\end{figure}

\begin{figure*}[htb]
\centerline{\includegraphics[width=0.75\linewidth]{fig/chipsort-bench-curves.pdf}}
\caption{Curves displaying the relative running time from each studied method. The ordinate represents the median of the measured running times divided by the input size at each test.}
\label{fig:bench-curves}
\end{figure*}

\section{Conclusion}
\label{sec:conclusion}
%
